# WEEK 5 Aggregate Logit (Coffee)
========================================================
---
title: "Sample Document"
output:
  html_document:
    toc: true
    theme: united
---

```{r}
COFFEE <- read.csv("CoffeeData.csv")

m1   <- lm(log(Share/Outside) ~ 0+Brand.1+Brand.2+Brand.3+Brand.4+Price+Feature+Display+F.D, data=COFFEE)
summary(m1); BIC (m1)

m2   <- lm(Price ~ 0+Brand.1+Brand.2+Brand.3+Brand.4+Feature+Display+F.D + Spot.1+Spot.2+Spot.3+Spot.4+Spot.5+Spot.6, data=COFFEE)
summary(m2)
```

Spot prices do a poor job in explaining the variance in price, p-values show that all but Spot.6 are poor predictors of Price

```{r}
m2.pred <- predict(m2)

m3   <- lm(log(Share/Outside) ~ 0+Brand.1+Brand.2+Brand.3+Brand.4+m2.pred+Feature+Display+F.D, data=COFFEE)
summary(m3); BIC (m3)
```

Using a 2 Stage Least Squares (Instrumental Variable) to predict market share, we find that the new model has a smaller BIC, indicating that the model is better.

Now that we can make a causal inference assuming no price endogenity we see that the price elasticity \( \beta_p \) is more negative, indicating a stronger sensitivity to price.

The 99% R^2 is suspicious.